---
layout: page
title:  "7-days #rstats"
---

These statistics are refreshed every day at midnight CET. The used scripts are on [github](https://github.com/calligross/twitteRstats). As always, pull requests are welcome.

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10, 
                      fig.path = 'figure/twitterstats-')
bots <- c('Rbloggers', 'RLangTip', 'CRANberriesFeed', 'R_Programming', 'SemanticEarth', 'BigDataTweetBot')
```

```{r libraries}
library(twitteR)
library(dplyr)
library(ggplot2)
library(grid)
library(png)
library(jpeg)
library(knitr)
```


```{r functions, eval=FALSE}
downloadUserPics <- function(Users, dir = '.') {
  downloadUserPic <- function(User, dir = '.') {
    url <- getUser(User)$toDataFrame()$profileImageUrl
    extension <- gsub('.*\\.', '', url)
    file <- paste0(dir, '/', User, '.', extension)
    download.file(url = url, destfile = file, quiet = TRUE)
    return(file)
  }
  sapply(Users, function(x) downloadUserPic(x))
}

rasterUserPics <- function(images) {
  extension <- gsub('.*\\.', '', images)
  rasters <- list()
  
  for (i in 1:length(images)) {
    if (extension[i] %in% c('jpg', 'jpeg')) {
      rasters[[images[i]]] <- readJPEG(images[i])
    }
  }
  return(rasters)
}

```

```{r}
# tweets <- Rtweets(since = '2016-04-22', n = 9999999)
# store_tweets_db(tweets)
register_sqlite_backend('tweets.db')
tweets <- load_tweets_db()
tweets_df <- twListToDF(tweets) %>% 
  filter(as.Date(created) >= (as.Date(Sys.Date()) - 7),
         as.Date(created) < as.Date(Sys.Date())) %>%
  mutate(text = iconv(text, 'UTF-8', 'ASCII', sub = ''))
```

## Most retweeted tweets (since `r Sys.Date() - 7`)

```{r MostRetweetedTweets}
tweets_df %>%
  filter(!screenName  %in% bots) %>%
  filter(isRetweet == FALSE) %>%
  filter(!grepl('^RT', text)) %>%
  mutate(Date = as.Date(created)) %>%
  group_by(Date) %>%
  filter(retweetCount == max(retweetCount)) %>%
  select(Date, retweetCount, screenName, text) %>%
  rename(`RT count` = retweetCount,
         User = screenName,
         Text = text) %>%
  kable(format = 'html')
```

## Most faved tweets (since `r Sys.Date() - 7`)

```{r MostFavedTweets}
tweets_df %>%
  filter(!screenName  %in% bots) %>%
  filter(isRetweet == FALSE) %>%
  filter(!grepl('^RT', text)) %>%
  mutate(Date = as.Date(created)) %>%
  group_by(Date) %>%
  filter(favoriteCount == max(favoriteCount)) %>%
  select(Date, favoriteCount, screenName, text) %>%
  rename(`Fav count` = favoriteCount,
         User = screenName,
         Text = text) %>%
  kable(format = 'html')
```

## Most active users (since `r Sys.Date() - 7`)

```{r MostTweetsByUser}
tweets_df %>%
  filter(!screenName  %in% bots) %>%
  filter(isRetweet == FALSE) %>%
  group_by(screenName) %>%
  summarise(n = n()) %>%
  ungroup %>%
  arrange(desc(n)) %>%
  slice(1:10) %>%
  rename(User = screenName, tweets = n) %>%
  mutate(User = paste0('[', User, '](http://twitter.com/', User, ')'),
         `No.` = 1:10) %>%
  select(`No.`, 1:2) %>%
  kable(format = 'markdown')

```

## Most retweeted users (since `r Sys.Date() - 7`)

```{r MostRetweetedUser}
tweets_df %>%
  filter(!screenName  %in% bots) %>%
  filter(isRetweet == FALSE) %>%
  group_by(screenName) %>%
  summarise(retweets = sum(retweetCount)) %>%
  ungroup %>%
  arrange(desc(retweets)) %>%
  slice(1:10) %>%
  mutate(screenName = factor(screenName, screenName)) %>%
  ggplot(aes(x = screenName, y = retweets)) +
  geom_bar(stat = 'identity') +
  theme_bw() + theme(axis.text.x = element_text(angle = 90))

```

## Most favourited users (since `r Sys.Date() - 7`)

```{r MostFavouritedUser}
tweets_df %>%
  filter(!screenName  %in% bots) %>%
  filter(isRetweet == FALSE) %>%
  group_by(screenName) %>%
  summarise(favourited = sum(favoriteCount)) %>%
  ungroup %>%
  arrange(desc(favourited)) %>%
  slice(1:10) %>%
  mutate(screenName = factor(screenName, screenName)) %>%
  ggplot(aes(x = screenName, y = favourited)) +
  geom_bar(stat = 'identity') +
  theme_bw() + theme(axis.text.x = element_text(angle = 90))

```

## Unique users per day (since `r Sys.Date() - 7`)

```{r TweetersPerDay}
tweets_df %>%
  filter(!screenName  %in% bots) %>%
  filter(isRetweet == FALSE) %>%
  mutate(Date = as.Date(created)) %>%
  group_by(Date) %>%
  summarise(Users = n_distinct(screenName)) %>%
  ggplot(aes(x = Date, y = Users)) +
  geom_line() +
  geom_point() +
  theme_bw()

```

## Number of tweets per day (since `r Sys.Date() - 7`)

```{r tweets per day}
tweets_df %>%
  filter(!screenName  %in% bots) %>%
  filter(isRetweet == FALSE) %>%
  mutate(Date = as.Date(created)) %>%
  group_by(Date) %>%
  summarise(Tweets = n()) %>%
  ggplot(aes(x = Date, y = Tweets)) +
  geom_line() +
  geom_point() +
  theme_bw()
```

